Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-11 method.tex
Minor changes to section 2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1023 ccdd05d5-56c1-461a-bf98-85f6876523b4

Here we describe a method for reducing the computational cost of a \TD\ search
for compact binary coalescence.  We give a truly zero-latency algorithm
that competes in terms of floating point operations per second with the
conventional \FD\ method, which requires a significant latency in order to be
computationally cheap. Our method, called \lloid{} (a backronym for
Low Latency Online Inspiral Detection),
involves two transformations of the template waveforms that produce a
smaller set of \emph{orthogonal} filters with far fewer coefficients than
 the original templates.

>>>>

Here we describe a method for reducing the computational cost of a \TD\ search
for compact binary coalescence.  We give a truly zero-latency algorithm
that competes in terms of floating point operations per second with the
conventional \FD\ method, which by contrast requires a significant latency due to the
inherent acausality of the Fourier transform.  Our method, called \lloid{}
(a backronym for Low Latency Online Inspiral Detection),
involves two transformations of the template waveforms that produce a
network of orthogonal filters that is far more computationally
efficient than the original bank of matched filters.
